```{r}
setwd('C:\\Users\\bfrickert\\Documents\\GitHub\\gadsdc2\\linear_assignment\\brian_linear')
ufo_model <- read.csv('ufo_model.tsv', sep='\t')
```

I am creating (at Aaron's suggestion) two sets of samples.
8000 that I've deemed as having had a sighting.
2000 where I've randomly setting a value of FALSE for Had.Sighting at a randomly selected time.


Now let's see if we can fit a logistic regression!

Ultimately, I don't do much better than an AUC score of over .50!!!!
(Although with one sample, I did see an AUC score of .68!!!)

```{r}
ufo_sighting <- ufo_model[sample(nrow(ufo_model),8000),]
ufo_sighting$Had.Sighting <- 1
ufo_nosighting <- ufo_model[sample(nrow(ufo_model),2000),]
ufo_nosighting$Had.Sighting <- 0
ufo_nosighting$Hour <- ufo_model[sample(nrow(ufo_model),2000),]$Hour
ufo_samples <- rbind(ufo_sighting, ufo_nosighting)
```

What is the distribution of distances from a UFO sighting (from a sample of 100) from the nearest 
Military Installation based on whether the UFO is round. Doesn't seem to be much difference.
```{r}
boxplot(MilitaryDist ~ is.Round, data=ufo_samples[sample(nrow(ufo_samples),100),], xlab="Distance From Military Insallation", ylab="Shape", horizontal=TRUE)
```
What is the distribution of distances from a UFO sighting (from a sample of 100) from the 
nearest airport based on whether the UFO is round.
```{r}
boxplot(AirportDist ~ is.Round, data=ufo_samples[sample(nrow(ufo_samples),100),], xlab="Airport Distance", ylab="Is Round?", horizontal=TRUE)
```
What is the distribution of distances from a UFO sighting (from a sample of 100) from the 
nearest meteorological station based on whether the UFO is round.
```{r}
boxplot(MeterologicalDist ~ is.Round, data=ufo_samples[sample(nrow(ufo_samples),100),], xlab="Meteorological Station Distance", ylab="Is Round?", horizontal=TRUE)
```
# Percentages of Roundess of UFO by state of UFO sighting's location.
```{r}
barplot(prop.table(table(ufo_samples$is.Round, ufo_samples$State), 2), xlab="State", ylab="Is Round")
```

```{r}
ufo_samples$Shape <- as.factor(ufo_samples$Shape)

model <- glm(Had.Sighting ~ State * Hour # (StorDist * GolfDist * MeterologicalDist) #+ SwampDist + LibDist + MallDist + HospitalDist + StorDist + GolfDist
             , data=ufo_samples, family="binomial")
summary(model)
```
Seeing the following Warning(!!):
Warning message:
 In predict.lm(object, newdata, se.fit, scale = 1, type = ifelse(type ==  :
   prediction from a rank-deficient fit may be misleading
```{r}
logodds <- predict(model, ufo_samples)
probs <- predict(model, ufo_samples, type="response")
head(logodds)
head(probs)
head(log(probs/(1-probs)))
head(exp(logodds)/(1+exp(logodds)))

head(data.frame(actual=ufo_samples$Had.Sighting, prediction=probs))

suppressPackageStartupMessages(library('ROCR'))
pred <- prediction(predictions=probs, labels=ufo_samples$Had.Sighting)
acc <- performance(pred, measure='acc')
plot(acc)
prec <- performance(pred, measure='prec')
plot(prec)
rec <- performance(pred, measure='rec')
plot(rec)
roc <- performance(pred, 'tpr', 'fpr')
plot(roc)
auc <- performance(pred, measure='auc')
auc@y.values[[1]]
```