---
title: "SimpleProjectViz"
output: html_document
---
Visualizations of NPR One Ratings Data

Data is in raw ratings format where each observation is a "rating" that a user has assigned to an individual story
relevant ratings can be one of the following: COMPLETE, THUMBUP, SHARE, SKIP, START

```{r}
df <- read.csv(file="ratings_story2014-09-10.csv")
df$ratings_origin <- as.character(df$ratings_origin)
```

The only origins (manual aggregations of stories) we care about are: INVEST, BREAK, OPENDOOR, SELECTS.  The only ratings we care about are SKIP, START, COMPLETED, SHARE, THUMBUP, PASS,

```{r}
origins <- c("INVEST","BREAK","OPENDOOR","SELECTS","ARCHIVES")
r <- df[df$ratings_origin %in% origins,]
relevant.ratings <- c("COMPLETED","THUMBUP","SHARE","SKIP","START","PASS")
r <- r[r$ratings_rating %in% relevant.ratings,]
```

Next we reshape the data into an aggregation by unique stories, adding the story ID as a rowname and some other munging.

```{r}
library(reshape2)
stories <- dcast(r, ratings_story_id + thing_title + thing_teaser + ratings_origin ~ ratings_rating, fun.aggregate=length)
rownames(stories) <- stories$ratings_story_id
stories <- stories[,2:ncol(stories)]
```


Now add some calculations into our stories dataframe for completion and incompletion percentage.  The ratings that indicate a positive response or what I'm calling a "completion" are COMPLETED, SHARE, and THUMBUP.  Incomplete Ratings are SKIP and START.

```{r} 
stories$TOTAL <- rowSums(stories[,-c(1,2,3,4)])
stories$incomplete_rate <- (stories$SKIP + stories$START + stories$PASS) / stories$TOTAL
stories$complete_rate <- (stories$COMPLETED + stories$THUMBUP + stories$SHARE) / stories$TOTAL
```

If the above returns the same values, we're ready to work with our data.  First let's plot the number of ratings for each story. This will give us a sense of the distribution of ratings for each story.

```{r}
boxplot(stories$TOTAL, cex=0.4)
```

Oh! We have lots of stories without a lot of ratings! Now lets separate the stories into the 5 origins we are interested in

```{r}
library(ggplot2)
p <- ggplot(stories, aes(ratings_origin, TOTAL))
p + geom_boxplot()
```

So we know that we have some stories that have too few ratings to get reliable data from. We also know we have quite a few stories with tons of data. Lets try removing the stories that have less than 25 ratings and then looking at the distribution again.

```{r}
stories.25 <- stories[stories$TOTAL >= 25,]
p2 <- ggplot(stories.25, aes(ratings_origin, TOTAL))
p2 + geom_boxplot()
```

Lets quickly compare the number of unique stories in each category

```{r}
p3 <- ggplot(stories.25, aes(ratings_origin))
p3 + geom_bar(stat="bin")
```

Thats a cleaner view of the distribution.  So we know that stories in BREAK, INVEST, and OPENDOOR have a median of about 1,000 ratings per story and SELECTS. 

So now lets compare the rates of assigning positive and negative ratings to each story and see how they perform compared to each other:

```{r}
p4 <- ggplot(stories.25, aes(ratings_origin,complete_rate))
p4 + geom_boxplot()

p5 <- ggplot(stories.25, aes(ratings_origin,incomplete_rate))
p5 + geom_boxplot()
```

One of the primary similary attribues I want to use for selecting k-nearest ratings by this user of similar stories is # of instances of similar words in the title and teaser. Let's make sure all stories have something substantial in those fields before moving to Python to do the CountVectorizing.

```{r}

stories.25$title_chars <- nchar(iconv(as.character(stories.25$thing_title, "latin1","UTF-8")))
stories.25$teaser_chars <- nchar(iconv(as.character(stories.25$thing_teaser,"latin1","UTF-8")))

boxplot(stories.25$title_chars, cex=0.4)
boxplot(stories.25$teaser_chars, cex=0.4)
```

We can conclude that the number of characters in both of the titles and teasers is sufficient to derive good count vectorizer analysis. Next time, after count vectorizing, I will get a sense for the number of similar number of stories which contain similar words, for any given story before deciding how to proceed with a deriving a distance function for k-nearest neighbor analysis.
